An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-06-18 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Optimization of PV systems is not a recent topic; since the $90$'s different techniques 
using a wide variety of criteria to find ultimate combinations for design parameters, 
based on intuitive, numerical and analytical methods were developed and evaluated \textcolor{red}{~\cite{Applasamy2011}}. 
An ideal combination of any PV system is made by the best compromise between 
two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.

@@

\textcolor{red}{The NPC or life-cycle cost is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime. The net present worth is found by discounting all cash inflows and outflows}, 
including cost of installation, replacement and maintenance of the PV system, 
at an internal rate of return (IRR)~\cite{Park2004}.  IRR is used to evaluate the attractiveness of a project or investment.

>>>>

Optimization of PV systems is not a recent topic; since the $90$'s different techniques 
using a wide variety of criteria to find ultimate combinations for design parameters, 
based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}. 
An ideal combination of any PV system is made by the best compromise between 
two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.

@@

The NPC or life-cycle cost is the present value of all the costs over the project lifetime, 
minus the present value of all the revenues that it earns over the project lifetime. 
The net present worth is found by discounting all cash inflows and outflows, 
including cost of installation, replacement and maintenance of the PV system, 
at an internal rate of return (IRR)~\cite{Park2004}.  IRR is used to evaluate the attractiveness of a project or investment.
